### 2018-01-09 submission/manuscript.Rmd
re-write second result paragraph

Using the Bray-Curtis distance metric, there was a significant difference across study in the bacterial community of fecal samples between carcinoma and controls, but not adenoma and controls [Table S4 & S5]. For studies with unmatched tissue samples a similar trend was observed [Table S3 & S4] while studies with tissue samples from the same individual (matched) had no differences [Table S6 & S7].

>>>>

Using the Bray-Curtis distance metric and PERMANOVA, it was possible to identify significant bacterial community changes, in specific studies, for both carcinoma versus control and adenoma versus control [Table S4 & S5]. Significant differences in bacterial community, assessed by PERMANOVA, were also identified in unmatched tissue samples (control and adenoma or carcinoma tissue not from the same individual) for both those with adenoma and carcinoma [Table S6 & S7]. For studies with matched samples (unaffected tissue and an adenoma or carcinoma from the same individual) no differences in bacterial community were observed when assessed with PERMANOVA [Table S6 & S7].

### 2018-01-09 submission/manuscript.tex
re-write second result paragraph

Using the Bray-Curtis distance metric, there was a significant
difference across study in the bacterial community of fecal samples
between carcinoma and controls, but not adenoma and controls {[}Table S4
\& S5{]}. For studies with unmatched tissue samples a similar trend was
observed {[}Table S3 \& S4{]} while studies with tissue samples from the
same individual (matched) had no differences {[}Table S6 \& S7{]}.

>>>>

Using the Bray-Curtis distance metric and PERMANOVA, it was possible to
identify significant bacterial community changes, in specific studies,
for both carcinoma versus control and adenoma versus control {[}Table S4
\& S5{]}. Significant differences in bacterial community, assessed by
PERMANOVA, were also identified in unmatched tissue samples (control and
adenoma or carcinoma tissue not from the same individual) for both those
with adenoma and carcinoma {[}Table S6 \& S7{]}. For studies with
matched samples (unaffected tissue and an adenoma or carcinoma from the
same individual) no differences in bacterial community were observed
when assessed with PERMANOVA {[}Table S6 \& S7{]}.
